\SW: Crowd-sourcing the Discovery of Gravitational Lenses. I: System Design

### 2013-04-10 doc/acknowledgments.tex
Text on identification analysis

We thank Brooke Simmons, David Hogg, XXX and YYY for many useful
conversations about citizen science and gravitational lens detection.
%
PJM was given support by the Royal  Society, in the form of a research
fellowship. He would like to thank the DotAstronomy community for
introducing so many valuable concepts and tools, and David Harris and
Roger Davies for valuable conversations about community-building.
%
% AV \ldots
%
% AM \ldots
%
% Zooniverse / Sloan Foundation.
%
The \sw project is open source, and was developed at
https://github.com/drphilmarshall/SpaceWarps.

>>>>

We thank all \Ncollaboration members of the \sw community for their
contributions to the project so far. A complete list of collaborators is
given at... In particular we would like to recognise the efforts of XXX,
YYY etc in moderating the discussion.

We are also grateful to Brooke Simmons, David Hogg, XXX and YYY for many
useful conversations about citizen science and gravitational lens
detection. % Need to cross-ref with Zooniverse author list
%
PJM was given support by the Royal  Society, in the form of a research
fellowship. 
% He would like to thank the DotAstronomy community for
% introducing so many valuable concepts and tools, and David Harris and
% Roger Davies for valuable conversations about community-building.
%
% AV \ldots
%
% AM \ldots
%
% Zooniverse / Sloan Foundation.
%
The \sw project is open source, and was developed at
https://github.com/drphilmarshall/SpaceWarps.

### 2013-04-10 doc/sw-system.tex
Text on identification analysis

\title[\sw I]
{\SW: Crowd-sourcing the Discovery of Gravitational Lenses. 
I: Experiment Design, and Testing with Simulated Data}

\author[The \SW Collaboration]{%
  The \SW Collaboration:
  Phil~Marshall,$^{1}$\thanks{\pjmemail}
  Aprajita Verma,$^{1}$
  Anupreeta More,$^{2}$
\newauthor{%
  Amit Kapadia,$^{3}$
  David Miller,$^{3}$
  Kelly Borden,$^{3}$
  Arfon Smith,$^{3}$}
\newauthor{%
  Elisabeth Baeten,
  Claude Cornen,
  Cecile Faure,
  Thomas Jennings,
  Rafael Kueng,$^{4}$}
\newauthor{%
  Christine Macmillan,
  Surhud More,$^{2}$
  Prasenjit Saha,$^{4}$
  Julianne Wilcox,
  Layne Wright}
  \medskip\\
  $^1$\oxford\\
  $^2$\ipmu\\
  $^3$\adler\\
  $^4$\zurich
}

@@

\item How quickly can lenses be detected? How many classifiers are
needed per target, and how quickly can they mobilise?

@@

In \Sref{sec:overview} we...

@@

@@

Presentation of images.

@@

\section{Analysis}
\label{sec:analysis}

Interpreting clicks. Online analysis: update model of each volunteer,
and estimate probability of classification.

Training data for tracking learning, and estimating completeness and
purity.

@@

\section{Results}
\label{sec:results}

@@

>>>>

\title[\sw I]
{\SW: Crowd-sourcing the Discovery of Gravitational Lenses. 
I: System Design}

\author[The \SW Collaboration]{%
  The \SW Collaboration:
  % \input{authors.tex}
}

@@

\item How quickly can lenses be detected, and non-lenses be rejected?
How many classifiers are needed per target, and how quickly can they
mobilise?

@@

In \Sref{sec:design} we introduce the \sw system, describing and
explaining its various features. We then briefly

@@

Unfamiliar objects: need to learn what lenses look like, fast. Rare
objects: need to be able to reject rapidly, and get through sample.
Confusion with non-lenses: further filtering via scientific discussion
and further classification (voting).

\subsection{Tutorial Material}
\label{sec:design:tutorial}

Learning what lenses do: Spotter's Guide and LensToy. Learning how
lenses work (science page, FAQ).

Inline tutorial. Merge into stream. Instant feedback, positive and
negative. Anecdotal support for this.

\subsection{The Classification Interface}
\label{sec:design:classification}

Image presentation. Consistency in size and appearance.

Interface fast due to pre-loading of images, and minimizing interaction.

Spotting lenses: Markers to be placed. Two reasons: first, to give good
feedback. Second, to improve quality of discussion later.

Quick dashboard provides simple ways to explore further: zoom, contrast
controls.

Non-lenses marked? Favourite button instead, enabling serendipitous
discovery of other interesting things, separate from lenses.

\subsection{Collaborative Filtering with ``Talk''}
\label{sec:design:classification}

Feeding in collections, following online analysis. 
Taking subjects to Talk individually, too.

Mental modeling. Further inspection on Dashboard. Voting.

Final sample generation.

@@

Presentation of images. Arcsinh stretch, calibration. Approximately
optimized.

@@

\section{Identification Analysis}
\label{sec:IDanalysis}

In this section we outline our methodology for interpreting the
interactions of the volunteers with the identification interface.  Each
classification made is logged in a database, storing subject IDs,
(anonymous) volunteer IDs, a timestamp and the classification results. 
The {\it kind} of subject -- whether it is a training subject (a 
simulated lens or a known non-lens) or a test subject (an unseen image
drawn from the survey) -- is also recorded. For all subjects, the
positions of all Markers are recorded, in pixel coordinates. For
training subjects, we also store the ``classification'' of the subject
as a lens, or a non-lens, and also the type of object present in the
image. These types are summarized in \Tref{tab:objecttypes}. 
This classification is used to provide instant feedback, but is also the
basic measurement used in a probabilistic classification of every
subject based on all image views to date.

We perform a ``Pseudo-online'' analysis of the classifications, 
updating a probabilistic model of every (anonymous) volunteer's
expertise, and every subject (in both the training and test sets), on a
daily basis. This allows us to track the speed with which the crowd
learns about lenses, and also gives us a dynamic estimate of the
posterior probability for  any given  subject being a lens, given all
classifications of it. Assigning thresholds in this lens probability
allows us to make good decisions about whether or not to accept a
subject into the collection of candidates visible in \Talk, and also
whether or not to  carry on classifying a subject at all.

In this paper we focus on the training data,  investigating  how the 
crowd's ability to identify gravitational lenses during the course of
the project, and the completeness and purity of the lens candidate
sample generated.

Where to describe probabilistic classifier stuff? Here or in an
appendix? Not sure.

@@

\section{Identification Results}
\label{sec:IDresults}

@@

Vary the acceptance and rejection thresholds, look at completeness and
purity as a function of this. How much time can be saved by retiring
subjects into candidate list or rejection list?
